Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-12 Thesis/chapter/03-theoretical-background.tex
ZrO2 ramble

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\ds{
\todo{Structure: Free writing} 
Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
Books PV, analytic otto? 
}
This chapter can be broken down into three section. 
The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
The second chapter reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties. 
%This chapter aims to shine light on the evolution of PV and on CIGSand 
%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
\subsection{Photovoltaics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored. 
Even though this time period is not exact and highly dependent on detection methods, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable options is \gls{pv}.

@@

\subsubsection{Crystalline Silicon Photovoltaics}
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.

\td{
what is it? 
What is it used for? 
How does it work? 
What different kinds are there? 
}

@@

{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
The standard substrate is glass \td{why?}. A flexible substrate is needed for a flexible module. 
Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \td{\gls{zro}}.
\begin{table}[htb]
    \center
    \begin{tabular}{cccc}
        \hline\hline
        Empirical Formula&    Name&   Band Gap&    Abbreviation\\
        \hline
        CuInSe2&       copper indium di selenide&  1&  CISe\\
        CuInS2&        copper indium di sulfide&  1.5&  CIS\\
        CuGaSe2&       copper gallium di selenide&  1.7&  CIGSe\\
        CuGaS2&        copper gallium di sulfide&  1.55&  CIGS\\
        \hline\hline
    \end{tabular}
	\caption{band gaps of different chalcopyrites}
	\label{tab:cigs}
\end{table}

%Um ein Modul flexibel zu machen kann statt Glas Stahl als stbstrat verwendet werden. 
%Allerdings wird ein Isolater zwischen Stahsubstrat und CIGS Zelle benötigt

\subsection{Zirconium oxide}
Zirconium oxide \td{(ZrO2)} is ceramic with a bandgap of 5-7 eV and dielectric constant of 15-22\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \td{PV} industry. 
It is monoclinic below 1170 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Stevens1986}.
%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
\td{what is important properites of zro2? }

>>>>

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\ds{what is it? What is it used for? How does it work? What different kinds are there? }
\ds{
\todo{Structure: Free writing} 
Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
Books PV, analytic otto? 
}
This chapter can be broken down into three section. 
The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
The second chapter reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties. 
%This chapter aims to shine light on the evolution of PV and on CIGSand 
%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
\subsection{Photovoltaics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored. 
Even though this time period is not exact and highly dependent on detection methods, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable options is \gls{pv}.

@@

\subsubsection{Crystalline Silicon Photovoltaics}
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
\td{what is it? What is it used for? How does it work? What different kinds are there? }

@@

\td{Bild: electrode + n-ZnO, [2.42eV] n-CdS 40nm, [1.15eV] p-CIGS 1.5um, Molybden 0.5 um, glass substrate, borrow book} 
The standard substrate is glass 
because of it's high thermal stability, resistance and hardness. 
A flexible substrate is needed for a flexible module, though. 
Plastics have a very low melting points and metals are conducting, but can be coated with a non conducting material such as \gls{zro}.
\begin{table}[htb]
    \center
    \begin{tabular}{cccc}
        \hline\hline
        Empirical Formula&    Name&   Band Gap&    Abbreviation\\
        \hline
		\ch{CuInSe2}&       copper indium di selenide&  1&  CISe\\
		\ch{CuInS2}&        copper indium di sulfide&  1.5&  CIS\\
		\ch{CuGaSe2}&       copper gallium di selenide&  1.7&  CIGSe\\
		\ch{CuGaS2}&        copper gallium di sulfide&  1.55&  CIGS\\
        \hline\hline
    \end{tabular}
	\caption{band gaps of different chalcopyrites}
	\label{tab:cigs}
\end{table}

\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage due to phase transition\cite{Nielsen2005}.
%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
It is not poisonous. \td{cite?}
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.

\td{what is important properites of zro2? }
\td{what is it? What is it used for? How does it work? What different kinds are there? }

\subsubsection{Sol-Gel}
\td{what is it? What is it used for? How does it work? What different kinds are there? }
One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
